---
title: "Data Analysis Report"
author: "Your Name"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    toc_float: true
    theme: cosmo
    highlight: tango
    code_folding: show
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
library(tidyverse)
library(knitr)
library(kableExtra)
```

## Executive Summary

Provide a brief overview of your analysis and key findings here.

## Introduction

### Objectives

- Objective 1: Describe your first analysis objective
- Objective 2: Describe your second analysis objective
- Objective 3: Describe your third analysis objective

### Data Description

Describe your dataset, including:

- Source of data
- Number of observations
- Number of variables
- Time period covered

## Data Loading and Preparation

```{r load-data}
# Load your data
# data <- read.csv("your_data.csv")

# Example with built-in dataset
data <- mtcars
```

### Data Structure

```{r data-structure}
str(data)
```

### Summary Statistics

```{r summary-stats}
summary(data) %>%
  kable() %>%
  kable_styling(bootstrap_options = c("striped", "hover"))
```

## Exploratory Data Analysis

### Univariate Analysis

```{r univariate}
# Distribution of key variables
ggplot(data, aes(x = mpg)) +
  geom_histogram(bins = 20, fill = "steelblue", color = "white") +
  theme_minimal() +
  labs(title = "Distribution of Miles Per Gallon",
       x = "MPG", y = "Frequency")
```

### Bivariate Analysis

```{r bivariate}
# Relationship between variables
ggplot(data, aes(x = wt, y = mpg)) +
  geom_point(color = "steelblue", size = 3) +
  geom_smooth(method = "lm", color = "coral") +
  theme_minimal() +
  labs(title = "MPG vs Weight",
       x = "Weight (1000 lbs)", y = "Miles Per Gallon")
```

### Correlation Analysis

```{r correlation}
# Correlation matrix
cor_matrix <- cor(data)
corrplot::corrplot(cor_matrix, method = "color", type = "upper")
```

## Statistical Analysis

### Hypothesis Testing

```{r hypothesis-test}
# Example t-test
t_test_result <- t.test(mpg ~ am, data = data)
print(t_test_result)
```

### Regression Analysis

```{r regression}
# Linear regression model
model <- lm(mpg ~ wt + hp + am, data = data)
summary(model)
```

## Results and Interpretation

Interpret your findings here. Discuss:

- Key patterns observed
- Statistical significance
- Practical implications
- Limitations of the analysis

## Conclusions

Summarize your main findings and recommendations.

## Appendix

### Session Info

```{r session-info}
sessionInfo()
```
