---
title: "Your Presentation Title"
subtitle: "Subtitle Goes Here"
author: "Your Name"
institute: "Your Organization"
date: "`r Sys.Date()`"
output:
  xaringan::moon_reader:
    css: [default, metropolis, metropolis-fonts]
    lib_dir: libs
    nature:
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
      ratio: '16:9'
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = FALSE,
  warning = FALSE,
  message = FALSE,
  fig.width = 10,
  fig.height = 6,
  fig.retina = 3
)

library(tidyverse)
library(knitr)
library(scales)

# Custom theme for plots
theme_presentation <- function() {
  theme_minimal(base_size = 16) +
    theme(
      plot.title = element_text(size = 20, face = "bold"),
      plot.subtitle = element_text(size = 14),
      axis.title = element_text(size = 14),
      legend.position = "bottom"
    )
}

# Load data
data <- mtcars
```

class: inverse, center, middle

# Welcome!

## Let's dive into the data

---

# Agenda

## Today's Topics

1. **Introduction** - Project overview and objectives

2. **Data Overview** - Key statistics and trends

3. **Analysis** - Detailed findings and insights

4. **Visualizations** - Interactive charts and graphs

5. **Conclusions** - Summary and recommendations

6. **Q&A** - Discussion and questions

---

class: inverse, center, middle

# Introduction

---

# Project Overview

## Objectives

.pull-left[
### Primary Goals

- Analyze key performance metrics
- Identify patterns and trends
- Generate actionable insights
- Support decision-making

]

.pull-right[
### Success Criteria

- Data quality > 95%
- Statistical significance
- Clear visualizations
- Actionable recommendations

]

---

# Why This Matters

## Business Impact

- **Cost Savings**: Potential to reduce expenses by X%

- **Efficiency Gains**: Improve processes by Y%

- **Strategic Insights**: Inform key business decisions

- **Competitive Advantage**: Stay ahead of industry trends

---

class: inverse, center, middle

# Data Overview

---

# Dataset Summary

```{r summary-stats}
summary_table <- data %>%
  summarise(
    Observations = n(),
    Variables = ncol(data),
    Avg_MPG = round(mean(mpg), 2),
    Avg_HP = round(mean(hp), 2),
    Avg_Weight = round(mean(wt), 2)
  ) %>%
  pivot_longer(everything(), names_to = "Metric", values_to = "Value")

kable(summary_table, format = "html", col.names = c("Metric", "Value"))
```

---

# Key Metrics

.pull-left[

```{r metric1, fig.height=5}
ggplot(data, aes(x = mpg)) +
  geom_histogram(bins = 15, fill = "#00BFC4", color = "white", alpha = 0.8) +
  labs(title = "Distribution of Fuel Efficiency",
       x = "Miles Per Gallon",
       y = "Frequency") +
  theme_presentation()
```

]

.pull-right[

### Insights

- Mean: **`r round(mean(data$mpg), 1)` MPG**
- Median: **`r round(median(data$mpg), 1)` MPG**
- Range: **`r round(min(data$mpg), 1)` - `r round(max(data$mpg), 1)`**

Most vehicles cluster around 15-25 MPG, with some high-efficiency outliers.

]

---

class: inverse, center, middle

# Analysis

---

# Correlation Analysis

```{r correlation, fig.width=10, fig.height=7}
cor_data <- data %>%
  select(mpg, cyl, disp, hp, wt, qsec) %>%
  cor()

corrplot::corrplot(cor_data, method = "color", type = "upper",
                   addCoef.col = "white", number.cex = 1.2,
                   tl.col = "black", tl.srt = 45, tl.cex = 1.2,
                   col = colorRampPalette(c("#F8766D", "white", "#00BFC4"))(200))
```

---

# Relationship: Weight vs Efficiency

```{r weight-mpg, fig.width=11, fig.height=6.5}
ggplot(data, aes(x = wt, y = mpg)) +
  geom_point(size = 4, alpha = 0.7, color = "#00BFC4") +
  geom_smooth(method = "lm", se = TRUE, color = "#F8766D", size = 1.5) +
  labs(title = "Vehicle Weight vs Fuel Efficiency",
       subtitle = "Strong negative correlation (r = -0.87)",
       x = "Weight (1000 lbs)",
       y = "Miles Per Gallon") +
  theme_presentation()
```

---

# Group Comparisons

.pull-left[

```{r transmission, fig.height=6}
data %>%
  mutate(Transmission = factor(am, labels = c("Automatic", "Manual"))) %>%
  ggplot(aes(x = Transmission, y = mpg, fill = Transmission)) +
  geom_boxplot(alpha = 0.7, width = 0.6) +
  geom_jitter(width = 0.15, alpha = 0.5, size = 2) +
  scale_fill_manual(values = c("#F8766D", "#00BFC4")) +
  labs(title = "Efficiency by Transmission",
       y = "Miles Per Gallon",
       x = "") +
  theme_presentation() +
  theme(legend.position = "none")
```

]

.pull-right[

### Key Findings

**Manual Transmission:**
- Average: 24.4 MPG
- Better efficiency
- Higher variability

**Automatic Transmission:**
- Average: 17.1 MPG
- Lower efficiency
- More consistent

Difference is statistically significant (p < 0.001)

]

---

# Statistical Model

```{r model}
model <- lm(mpg ~ wt + hp + am, data = data)
model_summary <- broom::tidy(model)

kable(model_summary,
      digits = 3,
      col.names = c("Variable", "Coefficient", "Std. Error", "t-value", "p-value"),
      format = "html")
```

### Model Performance

- **R-squared**: `r round(summary(model)$r.squared, 3)`
- **Adjusted R-squared**: `r round(summary(model)$adj.r.squared, 3)`
- **F-statistic**: `r round(summary(model)$fstatistic[1], 2)` (p < 0.001)

The model explains **`r round(summary(model)$r.squared * 100, 1)`%** of the variance in fuel efficiency.

---

class: inverse, center, middle

# Key Takeaways

---

# Main Findings

## 🎯 Three Critical Insights

1. **Weight is the strongest predictor**
   - Every 1000 lbs reduces efficiency by ~5 MPG
   - Strongest correlation among all variables

2. **Transmission type matters**
   - Manual transmission vehicles average 7 MPG better
   - Statistically significant difference

3. **Multiple factors interact**
   - Combined model provides best predictions
   - Weight, horsepower, and transmission all significant

---

# Recommendations

## 📋 Action Items

.pull-left[

### Immediate Actions

1. Focus on weight reduction strategies
2. Consider transmission options in design
3. Balance power with efficiency
4. Monitor key metrics continuously

]

.pull-right[

### Long-term Strategy

1. Invest in lightweight materials research
2. Optimize powertrain configurations
3. Develop predictive models
4. Set efficiency targets based on data

]

---

# Next Steps

## 🚀 Moving Forward

| Timeline | Action | Owner |
|----------|--------|-------|
| Week 1-2 | Validate findings with additional data | Analytics Team |
| Week 3-4 | Develop detailed implementation plan | Project Lead |
| Month 2 | Begin pilot program | Operations |
| Month 3 | Measure and report results | All Teams |

--

### Success Metrics

- Baseline established ✓
- Targets defined ✓
- Tracking system in place ✓

---

class: inverse, center, middle

# Thank You!

## Questions?

### Contact Information
Your Name | your.email@example.com | @yourhandle

---

# Appendix: Additional Resources

### Further Reading

- Detailed methodology documentation
- Statistical assumptions and tests
- Data dictionary and variable definitions
- Code repository and reproducibility guide

### Tools and Software

- **R** version `r getRversion()`
- **RMarkdown** for reproducible research
- **ggplot2** for visualizations
- **dplyr** for data manipulation
